CommonMind Consortium: DLPFC

### 2020-09-22 combined_analysis/diff.networks.Rmd
Update diff networks

# ASD
df_asd = fread(synGet('syn22343811')$path)
colnames(df_asd)[colnames(df_asd)=="Q‑Val" ] = 'Q'
df_asd2 = data.frame(ENSEMBL = df_asd$Gene, Q = df_asd$Q)
df_asd2$chisq = qchisq(df_asd2$Q + 1e-15, 1, lower.tail=FALSE)
rownames(df_asd2) = df_asd2$ENSEMBL

```

@@

	plot_module( mod, df_test.Dx_Sex, METADATA, dynamicColors.Dx_Sex, C.diff.discovery, resid.add[[resVersion]], variable, "MSSM-Penn-Pitt")   
	})

@@

```{r modules.in.second.cohort.Dx_Sex, fig.width=8, fig.height=80}

# i = which(df_cohort2$FDR < 0.1) 
i = 1:2

>>>>

# ASD
df_asd = fread(synGet('syn22343811')$path)
colnames(df_asd)[colnames(df_asd)=="Q‑Val" ] = 'Q'
df_asd2 = data.frame(ENSEMBL = df_asd$Gene, Q = df_asd$Q)
df_asd2$chisq = qchisq(df_asd2$Q + 1e-15, 1, lower.tail=FALSE)
rownames(df_asd2) = df_asd2$ENSEMBL
```

@@

	plot_module( mod, /, METADATA, dynamicColors.Dx_Sex, C.diff.discovery, resid.add[[resVersion]], variable, "MSSM-Penn-Pitt")   
	})

@@

```{r modules.in.second.cohort.Dx_Sex, fig.width=12, fig.height=40}

# i = which(df_cohort2$FDR < 0.1) 
i = 1
